Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-23 analysis/presentation/sim_survey_presentation.Rmd
Clue up draft of intro and start drafting the methods in the presentation

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September XX, 2018"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
---

@@

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
# load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")
```

## Fisheries-independent trawl surveys

<div class="columns-2">

@@

<br>
<img src="graphics/teleost_twitter_crop.jpg" width="400"/>
<font size="1"> 
&nbsp; <a href="https://twitter.com/coastguardcan/status/879410397790515201">@CoastGuardCAN</a>
</font>

</div>

## Fisheries-independent trawl surveys

<div class="columns-2">

How much survey effort is enough?

1. Sub-sampling
    - Truth unknown
    - Small sample size effect
2. Simulation
    - Truth controlled
    - Reality?

@@

<br>
<img src="graphics/teleost_twitter_crop.jpg" width="400"/>
<font size="1"> 
&nbsp; <a href="https://twitter.com/coastguardcan/status/879410397790515201">@CoastGuardCAN</a>
</font>

</div>

@@

- **Spatial aggregation**
- **Habitat preferences**
- **Survey design**

>>>>

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 6^th^, 2018"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
# load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

boat_txt <- '<br>
<img src="graphics/teleost_twitter_crop.jpg" width="400"/>
<font size="1"> 
<br>
&nbsp; <a href="https://twitter.com/coastguardcan/status/879410397790515201">Canadian Coast Guard | Twitter</a>
</font>'

```

## Fisheries-independent trawl surveys {.columns-2}

@@

```{r results = "asis"}
cat(boat_txt)
```

## Fisheries-independent trawl surveys {.columns-2}

- How much survey effort is enough?
    - Difficult to answer
        - Multi-stage sampling
        - Intra-haul correlation

@@

```{r results = "asis"}
cat(boat_txt)
```

## Multi-stage sampling

Surveys are generally designed to:

<font size="8"> 1 </font> | <font size="8"> 2 </font> | <font size="8"> 3 </font>
:----: | :----: | :----:
Conduct sets at multiple locations | Sub-sample catch for length measurements | Sub-sampling length groups for age determination
<img src="graphics/trawl_survey_crop.jpg" height="180"/> | <img src="graphics/cod_length.jpg" height="120"/> | <img src="graphics/Otoliths2_crop.jpg" height="140"/>

## Intra-haul correlation

Sampling clusters of fish that have similar characteristics (e.g. length)

- Results in samples with positive intra-haul correlation
    - Reduces effective sample size

<center> <img src="graphics/plos_figure_crop.png" height="300"/> 
<br>
<font size="1"> 
Graphic from <a href="http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1002915">Tunstrøm et al (2013) PLoS Comput Biol 9(2): e1002915.</a> 
</font>
</center>

## Fisheries-independent trawl surveys {.columns-2}

- How much survey effort is enough?
    - Attempt to answer using:
        - Sub-sampling
            - Based in reality
            - Truth unknown
        - Simulation
            - Truth known
            - Reality?

```{r results = "asis"}
cat(boat_txt)
```

@@

- **Dynamic abundance**
- **Spatial aggregation**
- **Survey design**
- **_Objective: build a simulation that emulates reality_**

## Step 1: Simulate abundance

- Common cohort model
    - $N_{a,y} = N_{a-1,y-1} e^{-Z_{a-1,y-1}}$
- First year filled via exponential decay
    -  $N_{a,1} = N_{a-1,1} e^{-Z_{a-1,1}}$
- Random-walk in recruitment
    - $log(N_{1,y}) = log(\mu_r) + \epsilon_{y}$, where $\epsilon_{y} \sim N(\epsilon_{y - 1}, \sigma_{r}^{2})$
- Total mortality correlated across ages and years
    - $log(Z_{a,y}) = log(\mu_Z) + \delta_{a,y}$, where $\delta_{a,y} \sim N(0, \Sigma_{a,y})$
        - Using covariance, $\Sigma_{a,y}$, described in Cadigan [-@Cadigan2016]

## References
